A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-04 paper.tex
Modify Introduction and move IOTA DM to related work

\section{Introduction}
%TODO: cite examples
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data marketplace is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

Among the challenges of data marketplace\cite{BigDataMarket}, we conclude the following four essential requirements of a data marketplace system:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of data marketplace should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

In contrast to centralized architectures in \cite{DIaas, IOTAIdustryMarketplace, MARSA} that target to handle static data sets, we proposed a decentralized data marketplace in \cite{MyDataMarketplace} which focuses on processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one. See Fig.~\ref{fig:system_design}.

In the previous paper, we investigated the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item Standing on our proposed decentralized data marketplace, we review several decentralized data marketplace architectures as well as the existing distributed storage, and clarify the necessity of using MAM.  
    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation. We also compare the perfomance of exchanging different cryptosystems.
	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:background}, the architecture of our proposed decentralized data marketplace is illustrated. In Section~\ref{section:relatedWork}, some related work of decentralized data marketplace, distributed data storage and use cases of MAM are analyzed. In Section ARCHI, the interactions of MAM and Ethereum Smart Contract in trading model is well explained. The analysis and improvement of MAM are given in Section MAM-EXP. In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully. Finally, we conclude the paper in Section CONCLUSION.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{system_design}
    \caption{The system design of a decentralized data marketplace which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.

@@

In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.

>>>>

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

Among the challenges of data trading platform\cite{BigDataMarket}, we conclude the following four essential requirements:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

In contrast to centralized architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a decentralized data trading infrastructure which aims for processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one. See Fig.~\ref{fig:system_design}.

We investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.  
    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation. We also compare the perfomance of exchanging different cryptosystems.
	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of data exchange mechanisms for IoT, decentralized data trading infrastructures and distributed data storage are analyzed. In Section ARCHI, the design thinking of proposed data trading architecture. In Section ARCHI, the trading models are well explained. The analysis and improvement of MAM are given in Section MAM-EXP. In Section OFFLOAD, the security issues and methods of offloading MAM operations to brokers will be discussed carefully. Finally, we conclude the paper in Section CONCLUSION.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{system_design}
    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

%TODO: cite IOTAIdustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.

@@

The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation is built on top of IOTA, which targets IoT data streams trading. Data streams are stored via MAM and data payment is paid in IOTA. Nevertheless, the platform design is centralized, where new devices require manual approval to be visible in the marketplace. In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.
